PANCHANGE_analysis

### 2020-12-17 PANCHANGE_analysis.Rmd
tweaked figure labelling for forest plots

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "comorbid depression and anxiety compared to control",
                             "depressive disorder compared to control",
                             "anxiety disorder compared to control",
                             "eating disorders compared to control",
                             "obsessive compulsive disorders compared to control",
                             "comorbid psychotic and bipolar disorder compared to control",
                             "psychotic disorder compared to control",
                             "bipolar disorder compared to control",
                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
                             "autism_spectrum_disorder compared to control",
                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
                             "mhd.personality_disorder compared to control",
                             "Female compared to male",
                             "Non-binary/Self-defined compared to male",
                             "16-18 compared to 26-35",
                             "19-25 compared to 26-35",
                             "36-45 compared to 26-35",
                             "46-55 compared to 26-35",
                             "56-65 compared to 26-35",
                             "66-70 compared to 26-35",
                             "71-75 compared to 26-35",
                             "76+ compared to 26-35",
                             "Mixed or multiple ethnicities compared to White",
                             "Asian compared to White",
                             "Black compared to White",
                             "Other compared to White",
                             "key_worker compared to employed",
                             "unemployed compared to employed",
                             "student compared to employed",
                             "retired compared to employed",
                             "time_diff_coping_lockdown_march_23")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Gender",
                  "Gender",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Other")

@@

```{r standardise linear variables}
lin_preds <- c("time_diff_coping_lockdown_march_23",
               "gad.sum_score_prepan",
               "phq.sum_score_prepan",
               "pcl.sum_score_prepan",
               "gad.sum_score_retro",
               "phq.sum_score_retro",
               "pcl.sum_score_retro"
               )

@@

model1b.lm.form("gad.sum_score_base", "gad.sum_score_prepan")
model1b.lm.form("gad.sum_score_base", "gad.sum_score_retro")

model1b.lm.form("phq.sum_score_base", "phq.sum_score_prepan")
model1b.lm.form("phq.sum_score_base", "phq.sum_score_retro")

model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_prepan")
model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_retro")

@@

gad.prepan.lm <-  lm(formula = gad.sum_score_base.gad.sum_score_prepan.glmformula,
                            dat.prepan)
gad.retro.lm <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
                            dat.retro)

phq.prepan.lm <-  lm(formula = phq.sum_score_base.phq.sum_score_prepan.glmformula,
                            dat.prepan)
phq.retro.lm <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
                            dat.retro)

pcl.prepan.lm <-  lm(formula = pcl.sum_score_base.pcl.sum_score_prepan.glmformula,
                            dat.prepan)
pcl.retro.lm <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
                            dat.retro)

@@

gad.retro.lm.glad <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
                            dat.retro.glad)
gad.retro.lm.nbr <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
                            dat.retro.nbr)
gad.retro.lm.ramp <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
                            dat.retro.ramp)

phq.retro.lm.glad <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
                            dat.retro.glad)
phq.retro.lm.nbr <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
                            dat.retro.nbr)
phq.retro.lm.ramp <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
                            dat.retro.ramp)

pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
                            dat.retro.glad)
pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
                            dat.retro.nbr)
pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
                            dat.retro.ramp)

@@

# prepandemic and retrospective, grouped by disorder measure
lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","GAD-7", "gad.prepan.lm.for.plot")
lmoutput_format(gad.retro.lm,"gad.sum_score_retro","GAD-7", "gad.retro.lm.for.plot")

lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","PHQ-9", "phq.prepan.lm.for.plot")
lmoutput_format(phq.retro.lm,"phq.sum_score_retro","PHQ-9", "phq.retro.lm.for.plot")

lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","PCL", "pcl.prepan.lm.for.plot")
lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","PCL", "pcl.retro.lm.for.plot")

# prepandemic and retrospective, grouped by time point
lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","Prepandemic", "gad.prepan.lm.for.plot.timegroup")
lmoutput_format(gad.retro.lm,"gad.sum_score_retro","Retrospective", "gad.retro.lm.for.plot.timegroup")

lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","Prepandemic", "phq.prepan.lm.for.plot.timegroup")
lmoutput_format(phq.retro.lm,"phq.sum_score_retro","Retrospective", "phq.retro.lm.for.plot.timegroup")

lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","Prepandemic", "pcl.prepan.lm.for.plot.timegroup")
lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","Retrospective", "pcl.retro.lm.for.plot.timegroup")

# Retrospective, grouped by sample
lmoutput_format(gad.retro.lm.glad,"gad.sum_score_retro","GLAD and EDGI", "gad.retro.lm.for.plot.GLAD")
lmoutput_format(gad.retro.lm.nbr,"gad.sum_score_retro","NBR", "gad.retro.lm.for.plot.NBR")
lmoutput_format(gad.retro.lm.ramp,"gad.sum_score_retro","RAMP", "gad.retro.lm.for.plot.RAMP")

lmoutput_format(phq.retro.lm.glad,"phq.sum_score_retro","GLAD and EDGI", "phq.retro.lm.for.plot.GLAD")
lmoutput_format(phq.retro.lm.nbr,"phq.sum_score_retro","NBR", "phq.retro.lm.for.plot.NBR")
lmoutput_format(phq.retro.lm.ramp,"phq.sum_score_retro","RAMP", "phq.retro.lm.for.plot.RAMP")

lmoutput_format(pcl.retro.lm.glad,"pcl.sum_score_retro","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
lmoutput_format(pcl.retro.lm.nbr,"pcl.sum_score_retro","NBR", "pcl.retro.lm.for.plot.NBR")
lmoutput_format(pcl.retro.lm.ramp,"pcl.sum_score_retro","RAMP", "pcl.retro.lm.for.plot.RAMP")

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=20, fig.width=20, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=20, fig.width=20, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by time point phq, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=20, fig.width=20, dpi=120}

@@

```{r forest plot by sample retro only pcl, fig.height=20, fig.width=20, dpi=120}

>>>>

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference: Employed)",
                  "Employment (Reference: Employed)",
                  "Employment (Reference: Employed)",
                  "Employment (Reference: Employed)",
                  "Other")

@@

```{r standardise linear variables}

## Create copies of the variables renamed

dat.prepan$GAD.prepandemic <- dat.prepan$gad.sum_score_prepan
dat.prepan$PHQ.prepandemic <- dat.prepan$phq.sum_score_prepan
dat.prepan$PCL.prepandemic <- dat.prepan$pcl.sum_score_prepan

dat.retro$GAD.retrospective <- dat.retro$gad.sum_score_retro
dat.retro$PHQ.retrospective <- dat.retro$phq.sum_score_retro
dat.retro$PCL.retrospective <- dat.retro$pcl.sum_score_retro

lin_preds <- c("time_diff_coping_lockdown_march_23",
               "GAD.prepandemic",
               "PHQ.prepandemic",
               "PCL.prepandemic",
               "GAD.retrospective",
               "PHQ.retrospective",
               "PCL.retrospective"
               )

@@

model1b.lm.form("gad.sum_score_base", "GAD.prepandemic")
model1b.lm.form("gad.sum_score_base", "GAD.retrospective")

model1b.lm.form("phq.sum_score_base", "PHQ.prepandemic")
model1b.lm.form("phq.sum_score_base", "PHQ.retrospective")

model1b.lm.form("pcl.sum_score_base", "PCL.prepandemic")
model1b.lm.form("pcl.sum_score_base", "PCL.retrospective")

@@

gad.prepan.lm <-  lm(formula = gad.sum_score_base.GAD.prepandemic.glmformula,
                            dat.prepan)
gad.retro.lm <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                            dat.retro)

phq.prepan.lm <-  lm(formula = phq.sum_score_base.PHQ.prepandemic.glmformula,
                            dat.prepan)
phq.retro.lm <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                            dat.retro)

pcl.prepan.lm <-  lm(formula = pcl.sum_score_base.PCL.prepandemic.glmformula,
                            dat.prepan)
pcl.retro.lm <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro)

@@

gad.retro.lm.glad <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                            dat.retro.glad)
gad.retro.lm.nbr <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                            dat.retro.nbr)
gad.retro.lm.ramp <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                            dat.retro.ramp)

phq.retro.lm.glad <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                            dat.retro.glad)
phq.retro.lm.nbr <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                            dat.retro.nbr)
phq.retro.lm.ramp <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                            dat.retro.ramp)

pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro.glad)
pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro.nbr)
pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro.ramp)

@@

# prepandemic and retrospective, grouped by disorder measure
lmoutput_format(gad.prepan.lm,"GAD.prepandemic","GAD-7", "gad.prepan.lm.for.plot")
lmoutput_format(gad.retro.lm,"GAD.retrospective","GAD-7", "gad.retro.lm.for.plot")

lmoutput_format(phq.prepan.lm,"PHQ.prepandemic","PHQ-9", "phq.prepan.lm.for.plot")
lmoutput_format(phq.retro.lm,"PHQ.retrospective","PHQ-9", "phq.retro.lm.for.plot")

lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","PCL", "pcl.prepan.lm.for.plot")
lmoutput_format(pcl.retro.lm,"PCL.retrospective","PCL", "pcl.retro.lm.for.plot")

# prepandemic and retrospective, grouped by time point
lmoutput_format(gad.prepan.lm,"GAD.prepandemic","Prepandemic", "gad.prepan.lm.for.plot.timegroup")
lmoutput_format(gad.retro.lm,"GAD.retrospective","Retrospective", "gad.retro.lm.for.plot.timegroup")

lmoutput_format(phq.prepan.lm,"PHQ.prepandemic","Prepandemic", "phq.prepan.lm.for.plot.timegroup")
lmoutput_format(phq.retro.lm,"PHQ.retrospective","Retrospective", "phq.retro.lm.for.plot.timegroup")

lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","Prepandemic", "pcl.prepan.lm.for.plot.timegroup")
lmoutput_format(pcl.retro.lm,"PCL.retrospective","Retrospective", "pcl.retro.lm.for.plot.timegroup")

# Retrospective, grouped by sample
lmoutput_format(gad.retro.lm.glad,"GAD.retrospective","GLAD and EDGI", "gad.retro.lm.for.plot.GLAD")
lmoutput_format(gad.retro.lm.nbr,"GAD.retrospective","NBR", "gad.retro.lm.for.plot.NBR")
lmoutput_format(gad.retro.lm.ramp,"GAD.retrospective","RAMP", "gad.retro.lm.for.plot.RAMP")

lmoutput_format(phq.retro.lm.glad,"PHQ.retrospective","GLAD and EDGI", "phq.retro.lm.for.plot.GLAD")
lmoutput_format(phq.retro.lm.nbr,"PHQ.retrospective","NBR", "phq.retro.lm.for.plot.NBR")
lmoutput_format(phq.retro.lm.ramp,"PHQ.retrospective","RAMP", "phq.retro.lm.for.plot.RAMP")

lmoutput_format(pcl.retro.lm.glad,"PCL.retrospective","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
lmoutput_format(pcl.retro.lm.nbr,"PCL.retrospective","NBR", "pcl.retro.lm.for.plot.NBR")
lmoutput_format(pcl.retro.lm.ramp,"PCL.retrospective","RAMP", "pcl.retro.lm.for.plot.RAMP")

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=30, fig.width=35, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=30, fig.width=30, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=30, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by time point phq, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by sample retro only pcl, fig.height=30, fig.width=30, dpi=120}
